### 2018-04-05 defectLocalization/paper/paper_body.tex
Update paper_body.tex
add some text to evaluation

We report the performance of the three models in table \ref{performance_top_k} .
For the project Zxing and SWT, because the their total of components is close to 10, we report the top-1 bug hit rate.
For the project AspectJ and Eclipse, given the their large  number of components, we report the top-10 bug hit rate.

@@

 			SWT(top-1) & 10(50\%) & 20(100\%) &18(90\%)\\

 			AspecJ(top-10) & 24(41.38\%)  & 46(79.31\%) & 28(48.28)\%\\

 			Eclipse(top-10) &22(3.6\%) & 124(20.29\%)& 26(4.26\%)\\

@@

>>>>

We report the performance of the three models in table \ref{performance_top_k}, \ref{performance_MRR} and \ref{performance_map}.
For the project Zxing and SWT, because the total of  their components is close to 10, we report the top-1 bug hit rate.
For the project AspectJ and Eclipse, given the large  number of components, we report the top-10 bug hit rate.
As shown in Table \ref{performance_top_k}, All models acheive 100\%  bug hit for the project ZXing, DRNN achieves the best result in all other three projects. It gets 100\%, 79.31\% and 20.29\% hit rate for the project SWT, AspectJ and Eclipse respectively. 
VSM achieves the lowest bug hit rate which is 50\%, 41.38\% and 3.6\% for SWT, AspectJ and Eclipse respectively. 
DRNN achieve 163.82\% more bugs hit on average than VSM.

@@

 			SWT(top-1) & 10(50\%) & \textbf{20(100\%)} &18(90\%)\\

 			AspecJ(top-10) & 24(41.38\%)  & \textbf{46(79.31\%)} & 28(48.28)\%\\

 			Eclipse(top-10) &22(3.6\%) & \textbf{124(20.29\%)} & 26(4.26\%)\\

@@

As shown in Table \ref{performance_MRR}, VSM achieves the best MRR of 43.12\% for ZXing, but DRNN achieves the best MRR in all other three projects which are 67.92\%, 44.10\% and 11.81\% for SWT, AspectJ and Eclipse respectively. 
DRNN achieve 163.82\% more bugs hit on average than VSM.
